---
title: README
author: Yingxin Xu
date: today
date-format: long
format: 
  html: 
    self-contained: true
    df-print: tibble
editor_options: 
  chunk_output_type: console
execute: 
  warning: false
  message: false
---

# Get libs

```{r, setup}
pacman::p_load(tidyverse, targets, gt, readxl, cowplot)
```

# Clean data

Data cleaning, including the following steps 

(The reason for placing the deletion of NA rows as the last step is that the majority of missing values occur in the 'runtime_minutes' column. However, this column does not affect our judgment of the highest-rated movie genres. Therefore, the choice is to extract the necessary data columns before removing the missing values.)

1. Select data rows where "movie_type" is either 'movie' or 'tvMovie' (tvMovie is also considered as movie).
2. Select rows where "Christmas" is TRUE.
3. Extract columns: primary_title, genres, average_rating, num_votes, and store them in the movie_clean data frame.
4. Delete rows in the data that contain NA values.
5. Sort data by avarage rating in descending order.

This is the cleaned data after the process:

```{r}
tar_read(movie_clean)
```

# Expanding Genres

Many movies belong to multiple genres at the same time. To analyse each genre individually, we have split the data of movies that belong to multiple genres into multiple rows. For instance, if a movie belongs to the Adventure, Crime, and Romance genres, the data for that movie is split into three rows. The "genres" entry for each of the three rows is Adventure, Crime, and Romance, respectively. The remaining data in primary_title, average_rating, and num_votes remains the same.

This approach allows us to calculate separate statistics such as the mean and median of average rating for each genre.

Below is the data obtained after splitting the genres entry.

```{r}
tar_read(movie_unlisted)
```

# Mean and Median Ratings for Each Genre

To identify the genre with the highest average rating, we examined the mean ratings for each genre. To mitigate the impact of skewness on our assessment, we also calculated the median ratings for each genre and generated box plots.

```{r}
tar_read(movie_mean) # get mean rating for each genre and sort decreasingly
tar_read(movie_median) # get median rating for each genre and sort decreasingly
tar_read(genre_maxmean) # select the top three genres with the highest mean ratings
tar_read(genre_maxmedian) # select the top three genres with the highest median ratings
```

Looking at the results, we can see that History is the genre with the highest average and median ratings, scoring 7.4 and 7.65, respectively. Documentary and War genres come right after. There is no skewness in the data.


# Boxplot and Table

Now, let's draw box plots to show how ratings are spread across different genres.

```{r}
tar_read(boxplot_movie)
```

Next, let's take a look at how many movies there are in each genre.

```{r}
tar_read(table_genre)
```

Looking at both the boxplot and the table, we can see that there's a big difference in the number of movies across various genres. Although History has the highest mean and median ratings, it doesn't have many movies in the dataset. On the other hand, genres like Comedy, Drama, Romance, and Family have a lot of Christmas movies.

It's worth noting that the Family genre has the highest rating for an individual movie. However, the average and median ratings for Family are not that high, probably because there are both high and low-rated movies in the mix.

# Top-rating Movies

Now, let's find out which Family movie holds the top rating.

```{r}
tar_read(movie_top)
```

The highest-rated movie is 'Bringing Back Christmas,' a family movie. However, it's worth noting that it has a relatively low number of votes, with only 20 people having rated it. This indicates that it's a less-popular movie.

Additionally, it's noteworthy that the num_votes for the top 15 movies based on average rating is less than 40 for each.

# Information about Top-rating Genre (History)

Next, let's look at the ratings and number of votes for the eight movies in the History genre.

```{r}
tar_read(genre_top)
```

Only the last movie has a low rating; all other movies have ratings above 6.9. The 4th movie has a large number of voters, indicating its popularity.

# Conclusion

We can draw the following conclusions:

1. Judging from the mean and median ratings, the best-rating genre for Christmas movies is History. Although there are only 8 Christmas movies in this genre, the majority of them have high ratings.

2. Looking at individual movie ratings, the highest-rated one belongs to the Family genre, titled 'Bringing Back Christmas.' However, it is unreasonable to determine the highest-rated genre based solely on individual movie ratings. So we can't say Family is the best-rating genre.

3. There is a correlation between the number of voters and movie ratings. According to the previous analysis, the top 15 movies with the highest average ratings all have a relatively low number of votes. We hypothesize that this could be due to individual taste variations, suggesting that as the number of voters increases, the average rating of movies might decrease. Consequently, high-rated and popular movies with a large voter base are relatively uncommon.

In summary, the 'History' genre gives the best average rating for Christmas movies.
